\sys: Light-touch Data-Parallel Shell Processing

### 2020-05-22 pldi/draft.tex
Quick resolution to make sure we can send a draft out

% For comments
\newcommand{\eat}[1]{}
\newcommand{\TODO}[1]{\hl{\textbf{TODO:} #1}\xspace}
\newcommand{\todo}[1]{\hl{#1}\xspace}
\newcommand{\fixme}[1]{[{\color{red}#1}]}
\newcommand{\nv}[1]{[{\color{cyan}nv: #1}]}
\newcommand{\kk}[1]{[{\color{magenta}kk: #1}]}
\newcommand{\km}[1]{[{\color{blue}km: #1}]}
\newcommand{\review}[1]{{\color{red}#1}}
\newcommand{\tr}[1]{} %% Text and comments for technical report

@@

To address this challenge, we develop \sys, a shell that parallelizes POSIX shell scripts. \kk{We need to mention data-parallelism earlier. We don't focus on general parallelization but rather data-parallelism (performing operations on disjoint partitions of the input and then merging the results. WE need to give a brief idea about that early on so that we don't create false ideas.}
% \kk{Mention that it outputs shell scripts.}
% \nv{I think the ``how'' it solves it should come later, we're still trying to convince them we solve it (see next sentences in this paragraph)
% \sys offers both classes of users in the second group such much-needed automation.
\sys benefits both programmer groups mentioned earlier, with a particular emphasis on users.
Command developers are provided a set of abstractions, akin to lightweight type annotations, for expressing the parallelizability properties of their commands:
  rather than providing a command's full observable behavior, these annotations focus primarily on their interaction with state.
Shell users, on the other hand, are provided full automation:
  \sys extracts parallelism latent in their scripts by analyzing their parallelizability properties. % of their fragments.
% benefiting scripting experts and non-experts alike by offering automated POSIX-aware parallelization of shell-scripts as long as command developers
\sys's transformations are conservative, in that they do not attempt to parallelize fragments that lack sufficient information---\ie at worst, \sys will choose to not improve performance rather than risking breakage.
% \kk{Should we mention that we only show this empirically?}
% \nv{I don't think so; I don't think this is the right point to talk about our evaluation, we just state our intention/high-level principles.}

>>>>

% For comments
\newcommand{\eat}[1]{}
\newcommand{\TODO}[1]{\hl{\textbf{TODO:} #1}\xspace}
\newcommand{\todo}[1]{\hl{#1}\xspace}
\newcommand{\fixme}[1]{{\color{red}#1}}
\newcommand{\nv}[1]{[{\color{cyan}nv: #1}]}
\newcommand{\kk}[1]{[{\color{magenta}kk: #1}]}
\newcommand{\km}[1]{[{\color{blue}km: #1}]}
\newcommand{\review}[1]{{\color{red}#1}}
\newcommand{\tr}[1]{} %% Text and comments for technical report

@@

To address this challenge, we develop \sys, a shell that extracts data-parallelism from POSIX shell scripts.
% \kk{We need to mention data-parallelism earlier. We don't focus on general parallelization but rather data-parallelism (performing operations on disjoint partitions of the input and then merging the results. WE need to give a brief idea about that early on so that we don't create false ideas.}
% \nv{First attempt here. I am trying to get a copy out ASAP, we can refine this later}
% \kk{Mention that it outputs shell scripts.}
% \nv{I think the ``how'' it solves it should come later, we're still trying to convince them we solve it (see next sentences in this paragraph)
% \sys offers both classes of users in the second group such much-needed automation.
\sys benefits both programmer groups, % mentioned earlier, 
  with a particular emphasis on users.
Command developers are provided a set of abstractions, akin to lightweight type annotations, for expressing the parallelizability properties of their commands:
  rather than providing a command's full observable behavior, these annotations focus primarily on their interaction with state.
Shell users, on the other hand, are provided full automation:
  \sys extracts parallelism latent in their scripts by analyzing their parallelizability properties. % of their fragments.
% benefiting scripting experts and non-experts alike by offering automated POSIX-aware parallelization of shell-scripts as long as command developers
\sys's transformations are conservative, in that they do not attempt to parallelize fragments that lack sufficient information---\ie at worst, \sys will choose to not improve performance rather than risking breakage.
% \kk{Should we mention that we only show this empirically?}
% \nv{I don't think so; I don't think this is the right point to talk about our evaluation, we just state our intention/high-level principles.}
